---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(tidyverse)
library(ggmedsl)
```
# ggmedsl

The goal of `ggmedsl` is to make the creation of MEDSL-themed plots seamless using `ggplot2` and a few functions. 

## Installation

You can install the latest version of `ggmedsl` from GitHub using `devtools`:

``` r
devtools::install_github("medsl/ggmedsl")
```

## Examples

The first function within `ggmedsl` is `medsl_plot`. This quickly formats a `ggplot2` object to render in MEDSL formatting. 

```{r example 1, fig.height=6, fig.width=6}
mtcars %>% 
  ggplot(aes(mpg, disp, color = factor(carb))) +
  geom_point(size = 3) +
  medsl_plot()
```

I have also created a number of color scales that follow the MEDSL color theme, `scale_color_medsl()`: 

```{r example 2, eval=FALSE, fig.height=6, fig.width=6, include=FALSE}
mtcars %>% 
  ggplot(aes(mpg, disp, color=factor(carb))) +
  geom_point(size=3) +
  medsl_plot() + scale_color_medsl()
```

